onsetsync: An R Package for Onset Synchrony Analysis

### 2023-05-13 paper/paper.Rmd
Fix typos and wrong citations types

`onsetsync` package comes with example performances from two traditions, Cuban Son and Salsa performances [@Poole_Tarsitani_Clayton_2022] and North Hindustani performances [@Clayton_Leante_Tarsitani_2021]. The examples are taken from the Interpersonal Entrainment in Music Performance (IEMP) project collection that has compiled small ensemble performance data from six traditions (North Indian ragas, Malian jembe, Tunisian stambeli, Uruguayan candombe, European string quartet, and Cuban son and salsa). These collection contain tens of hours annotated and verified onsets and are available from Open Science Framework (OSF). There are also noteworthy datasets containing audio and annotated contents of music relevant to assessing synchrony such as _Carnatic Music Rhythm Dataset_ [@srinivasamurthy2015particle], _Hindustani Music Rhythm Dataset_ [@srinivasamurthy2016generalized], _Arab-Andalusian (Maghreb) dataset_ [@sordo2014creating], _Scandinavian Fiddle Tunes with Accompanying Foot-Tapping_ [@lordelo2020adversarial] and _MAESTRO (MIDI and Audio Edited for Synchronous Tracks and Organisation)_ dataset which is an extensive collection (200+ hours) of professional piano performances [@hawthorne2018enabling]. Some datasets such as Chopin performances compiled by [@goebl2010investigations] facilitate study of the synchrony between the two hands of the pianist.

@@

Much of the research on synchrony in music has focused on
_sensorimotor synchronization_ (SMS) or just synchronization, a
processes occurring within 100-2000 ms timescales, which has commonly
been studied with tapping experiments [@repp2008sensorimotor, @repp2013sensorimotor] but also through analyses of music corpora, from string quartets [@wing2014optimal] to drum ensembles [@polak2016both] and to
Indian instrumental music performances [@clayton_et_al_2018b]. Synchronisation analyses can also be applied to field observations
such as the study of how walking drumming groups attempt to
resist synchronisation to the beats of other drum groups during their
walk across the city during a festival [@lucas2011inter].

>>>>

`onsetsync` package comes with example performances from two traditions, Cuban Son and Salsa performances [@Poole_Tarsitani_Clayton_2022] and North Hindustani performances [@Clayton_Leante_Tarsitani_2021]. The examples are taken from the Interpersonal Entrainment in Music Performance (IEMP) project collection that has compiled small ensemble performance data from six traditions (North Indian ragas, Malian jembe, Tunisian stambeli, Uruguayan candombe, European string quartet, and Cuban son and salsa). These collections contain tens of hours annotated and verified onsets and are available from Open Science Framework (OSF). There are also noteworthy datasets containing audio and annotated contents of music relevant to assessing synchrony such as _Carnatic Music Rhythm Dataset_ [@srinivasamurthy2015particle], _Hindustani Music Rhythm Dataset_ [@srinivasamurthy2016generalized], _Arab-Andalusian (Maghreb) dataset_ [@sordo2014creating], _Scandinavian Fiddle Tunes with Accompanying Foot-Tapping_ [@lordelo2020adversarial] and _MAESTRO (MIDI and Audio Edited for Synchronous Tracks and Organisation)_ dataset which is an extensive collection (200+ hours) of professional piano performances [@hawthorne2018enabling]. Some datasets such as Chopin performances compiled by @goebl2010investigations facilitate study of the synchrony between the two hands of the pianist.

@@

Much of the research on synchrony in music has focused on
_sensorimotor synchronization_ (SMS) or just synchronization, a
process occurring within 100-2000 ms timescales, which has commonly
been studied with tapping experiments [@repp2008sensorimotor, @repp2013sensorimotor] but also through analyses of music corpora, from string quartets [@wing2014optimal] to drum ensembles [@polak2016both] and to
Indian instrumental music performances [@clayton_et_al_2018b]. Synchronisation analyses can also be applied to field observations
such as the study of how walking drumming groups attempt to
resist synchronisation to the beats of other drum groups during their
walk across the city during a festival [@lucas2011inter].
